Hydras \& Co.

### 2023-07-12 doc/chapter-natural-deduction.tex
fix a case error (typically MacOS)
work on chapter-natural-deduction

\inputsnippets{folExamples/SysPrfEx2}

@@

We advise the reader to replay this proof on h.er.is computer
 in order to better understand its structure.

Let us give only a few comments.

@@

>>>>

\inputsnippets{FolExamples/SysPrfEx2}

@@

We advise the reader to replay this proof on h.er.is computer
 in order to better understand its structure, which we will only comment briefly.

@@

 \index{ackermann}{Projects}

\begin{project}[**]
  The type \texttt{SysPrf} has sort \texttt{Prop}, which prevent us from
extracting the underlying proof tree and its fringe from an hypothesis 
of the form $X\sdash f$. 
It would be nice (\emph{e.g.} for a better understanding of the proof of the deduction theorem) to be able to compute the the proof-tree built
by the proof of the deduction lemma. 
\end{project}
